---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 10pt
    geometry:
      - margin=1in
      - heightrounded
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
  fig.path = "figs/",
  fig.width = 7.252,
  fig.height = 4,
  comment = "#>",
  fig.retina = 3
)

source("functions.R")
```

\par\centering{\LARGE{Matthew Steven Krantz, MD}}
\par\centering{Division of Allergy, Pulmonary, and Critical Care Medicine}
\vspace{-5pt}
\par\centering{Vanderbilt University Medical Center}
\vspace{-5pt}
\par\centering{T-1218 Medical Center North}
\vspace{-5pt}
\par\centering{1161 21st Ave. S. Nashville, TN 37232-2650}
\vspace{-5pt}
\par\centering{{\large\Telefon} +1 (615) 322-6943}
\vspace{-5pt}
\par\centering{{\large\Letter} matthew.s.krantz@vumc.org}
\vspace{-5pt}
\par\centering{\href{http://www.mattkrantz.com}{mattkrantz.com}}

\vspace{-10pt}

# Education

\vspace{-10pt}
\begin{longtable}{lll}

    2012 & University of North Carolina, Chapel Hill, NC & BS Biology\\
    
    2016 & University of North Carolina, Chapel Hill, NC & MD Medicine\\

\end{longtable}

\vspace{-10pt}

# Post-Graduate Training

\vspace{-10pt}
\begin{longtable}{lll}

    2016 - 2024 & Vanderbilt University Medical Center, Nashville, TN & Residency Internal Medicine-Pediatrics\\
    
    2020 - 2024 & Vanderbilt University Medical Center, Nashville, TN & Fellowship Allergy-Immunology\\

\end{longtable}

\vspace{-10pt}

# Research Interests

- **Immunogenomics**

\vspace{-10pt}

# Teaching Interests

- **Clinical Drug Allergy**:

# Academic Appointments

\vspace{-10pt}
\begin{longtable}{llp{15cm}}
2025 - Present & \textbf{Vanderbilt University}, Nashville, TN & \\
 & Assistant Professor of Medicine, Division of Allergy, Pulmonary, and Critical Care Medicine\\[5pt]

2024 - 2025 & \textbf{Vanderbilt University}, Nashville, TN & \\
 & Instructor in Medicine, Division of Allergy, Pulmonary, and Critical Care Medicine\\
\end{longtable}

# Licensure and Certification

```{r}
library(dplyr)
library(here)
licensure_certifications <- read.csv(here("data", "licensure-certification.csv")) %>%
    arrange(desc(year_start)) %>%
  mutate(citation = paste0(description, " (", year_start, "-", year_end, ")"))
```

```{r}
#| results: asis

licensure_certifications %>% 
  pull(citation) %>% 
  make_bullet_list()
```

# Professional Organizations

```{r}
library(dplyr)
library(here)
professional_organizations <- read.csv(here("data", "professional-organizations.csv")) %>%
  mutate(citation = paste0(description))
```

```{r}
#| results: asis

professional_organizations %>% 
  pull(citation) %>% 
  make_bullet_list()
```

# Professional Activities

## Intramural
```{r}
library(dplyr)
library(here)
intramural <- read.csv(here("data", "professional-activities.csv")) %>%
    filter(category=="intramural") %>%
    arrange(desc(year_start)) %>%
  mutate(citation = paste0(description, " (", year_start, "-", year_end, ")"))
```

```{r}
#| results: asis

intramural %>% 
  pull(citation) %>% 
  make_bullet_list()
```

## Extramural

```{r}
library(dplyr)
library(here)
extramural <- read.csv(here("data", "professional-activities.csv")) %>%
    filter(category=="extramural") %>%
    arrange(desc(year_start)) %>%
  mutate(citation = paste0(description, " (", year_start, "-", year_end, ")"))
```

```{r}
#| results: asis

extramural %>% 
  pull(citation) %>% 
  make_bullet_list()
```

## Scientific Reviewer for Peer-Reviewed Journals

```{r}
library(dplyr)
library(here)
peer_review <- read.csv(here("data", "peer-review.csv")) %>%
  mutate(citation = paste0(description))
```

```{r}
#| results: asis

peer_review %>% 
  pull(citation) %>% 
  make_bullet_list()
```

# Honors, Awards, and Recognitions

```{r}
library(dplyr)
library(here)
awards <- read.csv(here("data", "honors-awards.csv")) %>% 
  arrange(desc(date)) %>% 
  mutate(citation = paste0(date, ": ", description))
```

```{r}
#| results: asis

awards %>% 
  pull(citation) %>% 
  make_bullet_list()
```

# Teaching Activities

# Research Program

# Articles in Peer-Reviewed Journals

## Original Research

```{r}
publications <- read.csv(here('data', 'publications.csv')) %>%
  mutate(
      author = str_replace(author, "\\bKrantz MS\\b", "**Krantz MS**"),
    journal  = ifelse(is.na(journal), '', paste0('_', journal, '_.')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    PMCID   = ifelse(is.na(number), '', PMCID),
    doi      = ifelse(
               is.na(doi), '',
               paste0('DOI: [', doi, '](', 'https://doi.org/', doi, ')')),
    title    = title,
    citation = paste0(author, ". ", title, ". ", journal, " ", date, ";", number, " ", doi, ". ", "PMID: ", PMID, "; ", "PMCID: ", PMCID, ".")
  ) %>% 
  arrange(desc(epub_date))
```

```{r}
#| results: asis

make_ordered_list_filtered(publications, "original_research")
```

## Reviews

```{r}
#| results: asis

make_ordered_list_filtered(publications, "reviews")
```

## Graphic Medicine

\vspace{-10pt}
