---
format:
  docx:
    reference-doc: Curriculum-Vitae-SOM-Format-8.2022-1.docx
    toc: false
    output-file: cv-krantz.docx
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false

library(dplyr)
library(here)
library(stringr)
library(lubridate)
source("functions.R")
```

# Name: Matthew Steven Krantz, MD, MS

Office Address: 2525 West End Ave, Suite 9500, Rm 9512, Nashville, TN 37203

Office Phone Number: +1 (615) 936-8415

Email: matthew.s.krantz@vumc.org

Lab Website: [krantzlab.org](http://krantzlab.org)



# Education

- **College:** University of North Carolina, Chapel Hill, NC. BS, 2012 (Biology with distinction; Minors: Chemistry, Writing for the Screen and Stage).
- **Professional:** University of North Carolina School of Medicine, Chapel Hill, NC. MD, 2016.
- **Graduate:** Vanderbilt University, Nashville, TN. MS, Biomedical Informatics, 2026.
- **Postgraduate Training:** Internship/Residency, Internal Medicine/Pediatrics, Vanderbilt University Medical Center, Nashville, TN, 2016–2020.
- **Postgraduate Training:** Fellowship, Allergy/Immunology, Vanderbilt University Medical Center, Nashville, TN, 2020–2024.

# Licensure and Certification

```{r}
licensure_certifications <- read.csv(here("data", "licensure-certification.csv")) %>%
  arrange(desc(year_start)) %>%
  mutate(citation = paste0(description, " (", year_start, "-", year_end, ")"))
```

```{r}
#| results: asis
licensure_certifications %>%
  pull(citation) %>%
  make_bullet_list()
```

# Academic Appointments

- 2025–Present: Assistant Professor of Medicine and Biomedical Informatics, Vanderbilt University, Nashville, TN.
- 2024–2025: Instructor in Medicine and Biomedical Informatics, Vanderbilt University, Nashville, TN.

# Professional Organizations

```{r}
professional_organizations <- read.csv(here("data", "professional-organizations.csv")) %>%
  mutate(citation = paste0(description))
```

```{r}
#| results: asis
professional_organizations %>%
  pull(citation) %>%
  make_bullet_list()
```

# Professional Activities

## Intramural

```{r}
intramural <- read.csv(here("data", "professional-activities.csv")) %>%
  filter(category == "intramural") %>%
  arrange(desc(year_start)) %>%
  mutate(citation = paste0(description, " (", year_start, "-", year_end, ")"))
```

```{r}
#| results: asis
intramural %>%
  pull(citation) %>%
  make_bullet_list()
```

## Extramural

```{r}
extramural <- read.csv(here("data", "professional-activities.csv")) %>%
  filter(category == "extramural") %>%
  arrange(desc(year_start)) %>%
  mutate(citation = paste0(description, " (", year_start, "-", year_end, ")"))
```

```{r}
#| results: asis
extramural %>%
  pull(citation) %>%
  make_bullet_list()
```

## Scientific Reviewer for Peer-Reviewed Journals

```{r}
peer_review <- read.csv(here("data", "peer-review.csv")) %>%
  mutate(citation = paste0(description))
```

```{r}
#| results: asis
peer_review %>%
  pull(citation) %>%
  make_bullet_list()
```

## Special Awards and Recognition

```{r}
awards <- read.csv(here("data", "honors-awards.csv")) %>%
  arrange(desc(date)) %>%
  mutate(citation = paste0(description, " (", date, ")"))
```

```{r}
#| results: asis
awards %>%
  pull(citation) %>%
  make_bullet_list()
```

# Teaching Activities

## Clinical Teaching

```{r}
clinical_teaching <- read.csv(here("data", "clinical-teaching.csv")) %>%
  arrange(desc(date_start)) %>%
  mutate(citation = paste0(name, ". ", institution, " (", date_start, "-", date_stop, ")"))
```

```{r}
#| results: asis
clinical_teaching %>%
  pull(citation) %>%
  make_bullet_list()
```

# Research Supervision

```{r}
research_supervision <- read.csv(here("data", "research-supervision.csv")) %>%
  arrange(desc(date_start)) %>%
  mutate(citation = paste0(name, ". ", institution, " (", date_start, "-", date_stop, ")"))
```

## PhD Students

```{r}
#| results: asis
research_supervision %>%
  filter(category == "phd-student") %>%
  pull(citation) %>%
  make_bullet_list()
```

## Clinical Fellows

```{r}
#| results: asis
research_supervision %>%
  filter(category == "clinical-fellow") %>%
  pull(citation) %>%
  make_bullet_list()
```

# Research Program

```{r}
grants <- read.csv(here("data", "grants.csv")) %>%
  mutate(
    project_start_date = as.Date(project_start_date, format = "%m/%d/%y"),
    project_end_date = as.Date(project_end_date, format = "%m/%d/%y"),
    project_start_date_formatted = format(project_start_date, "%m/%d/%y"),
    project_end_date_formatted = format(project_end_date, "%m/%d/%y"),
    title = enquote(paste0("[", title, "]", "(", url, ")")),
    citation = paste0(
      id, ". ", title, ". Source of Support: ", source_of_support,
      ". PI: ", pi_name, ". Total Award Amount: ", budget_total,
      ". Project Start and End Date: ", project_start_date_formatted, " - ", project_end_date_formatted
    )
  ) %>%
  arrange(desc(project_end_date))
```

## Current Grants — Principal Investigator

```{r}
#| results: asis
grants %>%
  filter(pi == 1) %>%
  pull(citation) %>%
  make_ordered_list()
```

## Pending — Co-Investigator

```{r}
#| results: asis
grants %>%
  filter(co_investigator == 1) %>%
  pull(citation) %>%
  make_ordered_list()
```

# Publications and Presentations

## Articles in Peer-Reviewed Journals

```{r}
publications <- read.csv(here("data", "publications.csv")) %>%
  mutate(
    epub_date = as.Date(epub_date, format = "%m/%d/%y"),
    author = str_replace(author, "\\bKrantz MS\\b", "**Krantz MS**"),
    journal = ifelse(is.na(journal), "", paste0("_", journal, "_.")),
    number = ifelse(number == "", "", paste0(number, ".")),
    PMID = ifelse(number == "", "", paste0("PMID: ", PMID, ".")),
    PMCID = ifelse(PMCID == "", "", paste0("PMCID: ", PMCID, ".")),
    doi = ifelse(
      doi == "", "",
      paste0("DOI: [", doi, "](", "https://doi.org/", doi, ")")
    ),
    title = title,
    citation = paste0(author, ". ", title, ". ", journal, " ", date, ";", number, " ", doi, ". ", PMID, " ", PMCID)
  ) %>%
  arrange(desc(epub_date))
```

### Original Research

```{r}
#| results: asis
make_ordered_list_filtered(publications, "original_research")
```

### Reviews

```{r}
#| results: asis
make_ordered_list_filtered(publications, "reviews")
```

### Invited Editorials

```{r}
#| results: asis
make_ordered_list_filtered(publications, "invited_editorials")
```

### Case Reports

```{r}
#| results: asis
make_ordered_list_filtered(publications, "case_reports")
```

## Book Chapters

```{r}
book_chapters <- read.csv(here("data", "book-chapters.csv")) %>%
  mutate(
    author = str_replace(author, "\\bKrantz MS\\b", "**Krantz MS**"),
    book_title = ifelse(is.na(book_title), "", paste0("_", book_title, "_")),
    chapter_title = enquote(chapter_title),
    citation = paste0(author, ". ", "(", date, ") ", chapter_title, " in ", editor, " (ed.) ", book_title, ". ", place, ": ", publisher, ".")
  ) %>%
  arrange(desc(date))
```

```{r}
#| results: asis
make_ordered_list_filtered(book_chapters, "book_chapters")
```

## Graphic Medicine

```{r}
graphic_medicine <- read.csv(here("data", "graphic-medicine.csv")) %>%
  mutate(
    epub_date = as.Date(epub_date, format = "%m/%d/%y"),
    author = str_replace(author, "\\bKrantz MS\\b", "**Krantz MS**"),
    journal = ifelse(is.na(journal), "", paste0("_", journal, "_.")),
    number = ifelse(is.na(number), "", paste0(number, ".")),
    PMCID = ifelse(is.na(number), "", PMCID),
    doi = ifelse(
      is.na(doi), "",
      paste0("DOI: [", doi, "](", "https://doi.org/", doi, ")")
    ),
    title = title,
    citation = paste0(author, ". ", title, ". ", journal, " ", date, ";", number, " ", doi, ". ", "PMID: ", PMID, "; ", "PMCID: ", PMCID, ".")
  ) %>%
  arrange(desc(epub_date))
```

```{r}
#| results: asis
make_ordered_list_filtered(graphic_medicine, "graphic_medicine")
```

## Media

```{r}
media <- read.csv(here("data", "media.csv")) %>%
  arrange(desc(date)) %>%
  mutate(
    date = format(date, format = "%b %d, %Y"),
    outlet = paste0("**", outlet, "**"),
    citation = paste0(date, ", ", outlet, ": ", post, ".")
  )
```

```{r}
#| results: asis
media %>%
  pull(citation) %>%
  make_ordered_list()
```

## Presentations at Scientific Meetings

```{r}
presentations <- read.csv(here("data", "presentations.csv")) %>%
  arrange(desc(date)) %>%
  mutate(
    with = ifelse(is.na(with), "", paste0(", with ", with)),
    title = paste0(enquote(title), with),
    title = ifelse(is.na(series), title, paste(title, series, sep = ". ")),
    date = as.Date(date, format = "%m/%d/%y"),
    date_formatted = format(date, format = "%b %d, %Y"),
    citation = paste(title, host, location, date_formatted, sep = ". ")
  )
```

### Invited Speaker

```{r}
#| results: asis
make_ordered_list_filtered(presentations, "invited")
```
